---
title: "testPrecursorWindows"
author: "xyz"
date: '2022-06-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr)
library(Aerith)
library(stringr)
library(ggpointdensity)
```

```{r}
# user  system elapsed
# 81.407   7.750 117.657
system.time(
  sip <-
    readFilesScansTopPSMs("/mnt/d/ubuntuShare/EcoliSIP/C13pct25orbit90min/sip/", 5)
)
# user  system elapsed
# 84.734   7.110 118.080
system.time(
  ThreDf <-
    getFilterThresholdTopPSMs("/mnt/d/ubuntuShare/EcoliSIP/C13pct25orbit90min/sip/", 0.01, 1)
)

sum(ThreDf$threshold$pepCount)

sip <- ThreDf$topPSMs
thre <- ThreDf$threshold
sipGood <- rbind(
  sip[sip$parentCharges == 2 &
    sip$scores >= thre$scoreThreshold[1], ],
  sip[sip$parentCharges == 3 &
    sip$scores >= thre$scoreThreshold[2], ],
  sip[sip$parentCharges > 3 &
    sip$scores >= thre$scoreThreshold[3], ]
)
table(round(
  sipGood$measuredParentMasses - sipGood$calculatedParentMasses
))
```

### topN=5

```{r}
system.time(
  ThreDf <-
    getFilterThresholdTopPSMs("/mnt/d/ubuntuShare/EcoliSIP/C13pct25orbit90min/sip/", 0.01, 5)
)
sum(ThreDf$threshold$pepCount)

sipGood <- ThreDf$topPSMs[ThreDf$topPSMs$scores >= ThreDf$threshold$scoreThreshold[1], ]
```

### mass windows and peptide length

Pearson's product-moment correlation

data:  windows and pepLength
t = 76.815, df = 30441, p-value < 2.2e-16
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 0.3934903 0.4123096
sample estimates:
      cor 
0.4029425 

```{r}
neutronMass <- 1.003355
sipGoodWindows <- sipGood

windows <-
  sipGoodWindows$measuredParentMasses - sipGoodWindows$calculatedParentMasses
sign <- ifelse(windows > 0, 1, -1)
windows <-
  abs(windows) %/% neutronMass

MassError <-
  abs(sipGoodWindows$measuredParentMasses - sipGoodWindows$calculatedParentMasses) %% neutronMass
windows <-
  ifelse(MassError >= 0.5,
    windows + 1,
    windows
  )
windows <- windows * sign
sipGoodWindows$Windows <- windows

MassError <-
  ifelse(MassError >= 0.5,
    neutronMass - MassError,
    MassError
  )
sipGoodWindows$MassError <- MassError

pepLength <-
  str_length(str_sub(str_extract(sipGood$identifiedPeptides, "\\[.*\\]"), 2, -2))
drawDf <- data.frame(Windows = windows, PeptideLength = pepLength)

ggplot(drawDf, aes(x = PeptideLength, y = Windows)) +
  geom_pointdensity(method = "default") +
  scale_color_continuous(type = "viridis") +
  theme(text = element_text(size = 15)) +
  scale_x_continuous(breaks = seq(0, max(pepLength), by = 1)) +
  scale_y_continuous(breaks = seq(min(windows), max(windows), by = 1)) +
  theme_bw()
ggsave("mass windows and peptide length.pdf",
  width = 12,
  height = 8
)
cor.test(windows, pepLength)

ggplot(drawDf, aes(x = PeptideLength, y = MassError)) +
  geom_pointdensity() +
  scale_color_continuous(type = "viridis") +
  theme(text = element_text(size = 15)) +
  scale_x_continuous(breaks = seq(0, max(pepLength), by = 1)) +
  # scale_y_continuous(breaks = seq(min(windows), max(windows), by = 1)) +
  theme_bw()
ggsave("mass error and peptide length.pdf",
  width = 12,
  height = 8
)
cor.test(MassError, pepLength)

ggplot(drawDf, aes(x = windows, y = MassError)) +
  geom_pointdensity() +
  scale_color_continuous(type = "viridis") +
  theme(text = element_text(size = 15)) +
  scale_x_continuous(breaks = seq(min(windows), max(windows), by = 1)) +
  # scale_y_continuous(breaks = seq(min(windows), max(windows), by = 1)) +
  theme_bw()
ggsave("mass error and mass windows.pdf",
  width = 12,
  height = 8
)
cor.test(MassError, windows)
```

### get accurate precursor mass

```{r}
ProtonMass <- 1.007276466
charges <- sipGood$parentCharges
pepSeqs <-
  str_sub(str_extract(sipGood$identifiedPeptides, "\\[.*\\]"), 2, -2)
pcts <- sipGood$searchNames
pcts <-
  as.numeric(str_sub(str_split(pcts, "_", simplify = T)[, 2], 1, -4)) / 100
getSeqMass <- function(pepSeq, pct) {
  spectra <- precursor_peak_calculator_DIY(pepSeq, "C13", pct)
  mass <- spectra$Mass[which.max(spectra$Prob)]
  return(mass)
}
accurateMasses <- mapply(getSeqMass, pepSeqs, pcts)

sipGoodWindows <- sipGood
sipGoodWindows$calculatedParentMasses <- accurateMasses

windows <-
  sipGoodWindows$measuredParentMasses - sipGoodWindows$calculatedParentMasses
sign <- ifelse(windows > 0, 1, -1)
windows <-
  abs(windows) %/% neutronMass

MassError <-
  abs(sipGoodWindows$measuredParentMasses - sipGoodWindows$calculatedParentMasses) %% neutronMass
windows <-
  ifelse(MassError >= 0.5,
    windows + 1,
    windows
  )
windows <- windows * sign
sipGoodWindows$Windows <- windows

MassError <-
  ifelse(MassError >= 0.5,
    neutronMass - MassError,
    MassError
  )
sipGoodWindows$MassError <- MassError

drawDf <- data.frame(Windows = windows, PeptideLength = pepLength)
ggplot(drawDf, aes(x = PeptideLength, y = Windows)) +
  geom_pointdensity(method = "default") +
  scale_color_continuous(type = "viridis") +
  theme(text = element_text(size = 15)) +
  scale_x_continuous(breaks = seq(0, max(pepLength), by = 1)) +
  scale_y_continuous(breaks = seq(min(windows), max(windows), by = 1)) +
  theme_bw()
ggsave("real mass windows and peptide length.pdf",
  width = 12,
  height = 24
)
cor.test(windows, pepLength)
```

### decoy

```{r}
decoy <- sipGoodWindows[str_detect(sipGoodWindows$proteinNames, "Rev_"), ]
```

### Averagine

#### simulate mass window center

percent:

0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99,100

center:

0,0,1,1,2,2,3,4,4,5,5,6,6,7,7,8,9,-2,-1,-1,0,0,1,1,2,3,3,4,4,5,5,6,7,7,-3,-3,-2,-2,-1,-1,0,1,1,2,2,3,3,4,4,5,-5,-5,-4,-4,-3,-3,-2,-1,-1,0,0,1,1,2,2,3,4,-7,-6,-6,-5,-5,-4,-4,-3,-2,-2,-1,-1,0,0,1,2,2,-8,-8,-7,-7,-6,-6,-5,-4,-4,-3,-3,-2,-2,-1,-1,0,0

center after moving average: 

0,0,1,1,2,2,3,4,4,5,5,6,6,7,7,6,4,3,1,-1,0,0,1,1,2,3,3,4,4,5,5,6,4,3,1,-1,-2,-2,-1,-1,0,1,1,2,2,3,3,4,2,1,-1,-3,-4,-4,-3,-3,-2,-1,-1,0,0,1,1,2,2,1,-1,-2,-4,-6,-5,-5,-4,-4,-3,-2,-2,-1,-1,0,0,1,-1,-2,-4,-6,-7,-7,-6,-6,-5,-4,-4,-3,-3,-2,-2,-1,-1,0,0

```{r}
getResidueMass <- function(residue, pct) {
  spectra <- residue_peak_calculator_DIY(residue, "C13", pct)
  mass <- spectra$Mass[which.max(spectra$Prob)]
  return(mass)
}
# get precursor mass by sum of highest peak mass of residue
monoAveragineSeqs <- rep("a", 101)
pcts <- seq(0, 100) / 100
monoAveragineMasses <-
  mapply(getResidueMass, monoAveragineSeqs, pcts)
monoAveragineMassMat <- 6:60 %*% t(monoAveragineMasses)
colnames(monoAveragineMassMat) <- pcts
rownames(monoAveragineMassMat) <- 6:60
monoAveragineMassMat <-
  monoAveragineMassMat + getResidueMass("Nterm", 0) + getResidueMass("Cterm", 0)

# get precursor mass by accurate calculation
pcts <- seq(0, 100) / 100
pcts <- rep(pcts, each = 60 - 6 + 1)
monoAveragineSeqs <- strrep("a", 6:60)
monoAveragineSeqs <- rep(monoAveragineSeqs, 101)
AveragineMasses <- mapply(getSeqMass, monoAveragineSeqs, pcts)
AveragineMassesMat <- matrix(AveragineMasses, nrow = 60 - 6 + 1)
colnames(AveragineMassesMat) <- seq(0, 100) / 100
rownames(AveragineMassesMat) <- 6:60

# get window shift
windowsMat <- (AveragineMassesMat - monoAveragineMassMat)
write.csv(windowsMat, "windowsMat.csv")
pdf("AveragineMass and monoAveragineMass.pdf")
plot(x = 0:100, y = AveragineMassesMat["11", ], type = "l", col = "red")
lines(x = 0:100, y = monoAveragineMassMat["11", ], type = "l", col = "green")
dev.off()
# get peptides with 11 residues' mass center
center <- round(windowsMat["11", ])
paste(names(center), collapse = ",")
paste(unname(center), collapse = ",")
paste(0:100, collapse = ",")
pdf("pct and mass window center.pdf")
plot(x = 0:100, y = center)
dev.off()

# there is abrupt change of center
# for example pct 49 and pct 50 of 11 residue peptide
# use moving average to soft it
ma <- function(x, n = 5) {
  filter(x, rep(1 / n, n), sides = 2)
}
paste(round(ma(center, n = 5)), collapse = ",")
```

#### simulate masswindow length

percent:

0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99,100

half width:

2,2,2,3,4,4,4,5,4,5,6,6,6,6,6,6,6,6,6,6,7,7,7,8,7,8,7,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,8,7,8,7,7,7,7,6,7,6,6,6,6,6,6,6,6,6,5,5,4,4,4,4,4,3,3,2

longer half width:

2,3,3,4,5,5,6,7,6,7,7,8,7,8,8,8,9,9,9,9,9,9,9,10,9,10,9,10,10,10,10,10,10,11,10,11,10,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,11,10,11,10,11,10,10,10,9,10,9,9,9,9,9,9,9,8,9,8,8,8,7,7,7,7,7,6,6,5,5,5,4,4,2

```{r}
getSeqMassWidth <- function(pepSeq, pct) {
  spectra <- precursor_peak_calculator_DIY(pepSeq, "C13", pct)
  return(sum(spectra$Prob > 0.01))
}
pcts <- seq(0, 100) / 100
pcts <- rep(pcts, each = 60 - 6 + 1)
monoAveragineSeqs <- strrep("a", 6:60)
monoAveragineSeqs <- rep(monoAveragineSeqs, 101)
AveragineWidth <- mapply(getSeqMassWidth, monoAveragineSeqs, pcts)
AveragineWidthMat <- matrix(AveragineWidth, nrow = 60 - 6 + 1)
colnames(AveragineWidthMat) <- seq(0, 100) / 100
rownames(AveragineWidthMat) <- 6:60
# get peptides with 11 residues' mass width
width <- round(AveragineWidthMat["11", ]/2)
# let the width longer
# width <- round(AveragineWidthMat["11", ] / 1.5)
paste(names(width), collapse = ",")
paste(unname(width), collapse = ",")
paste(0:100, collapse = ",")
```

### generate configs with different mass center

```{r}
generateOneCFG("/mnt/d/Projects/Aerith/extdata/SiprosConfigN15SIP.cfg", "configs", "N", 50, -3, 7)
generateCFGs("/mnt/d/Projects/Aerith/extdata/SiprosConfigN15SIP.cfg", "configs", "C")
```
